Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-17 paper/paper.tex
fix

\Luc{"RCE refers to the process by which an agent can exploit a network vulnerability to run arbitrary code on a targeted machine or system. In an RCE attack, hackers intentionally exploit a remote code execution vulnerability to run malware. By prompting the targeted device to perform code execution, a hacker can run their own programming in its place. This programming can then enable them to gain full access, steal data, carry out a full distributed denial of service (DDoS) attack, destroy files and infrastructure, or engage in illegal activity. And as the term remote execution suggests, an RCE cyberattack can take place from any geophysical location."\\ Texto copiado de:  https://www.solarwindsmsp.com/blog/remote-code-execution \\

>>>>

\Luc{"RCE refers to the process by which an agent can exploit a network vulnerability to run arbitrary code on a targeted machine or system. In an RCE attack, hackers intentionally exploit a remote code execution vulnerability to run malware. By prompting the targeted device to perform code execution, a hacker can run their own programming in its place. This programming can then enable them to gain full access, steal data, carry out a full distributed denial of service (DDoS) attack, destroy files and infrastructure, or engage in illegal activity. And as the term remote execution suggests, an RCE cyberattack can take place from any geophysical location."\\ Texto copiado de:  https://www.solarwindsmsp.com/blog/remote-code-execution} \\
